\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-05 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Sec. V.B with 50 generator simulation, 100 dim state space

We mention here that (\ref{ItoSDEvectorlevel}) has been used in \cite{ju2018analytical,ju2018stochastic} for uncertainty propagation via stochastic averaging approximation where the univariate energy PDF was proposed as a ``proxy" for the entire joint PDF. Most relevant to our approach in the power systems literature is the work in \cite{wang2013fokker}, which indeed voiced the need for computing the transient joint PDFs but only dealt with the single-machine-infinite-bus case -- simplest ($n=1$) instance of (\ref{ItoSDEvectorlevel}). The resulting bivariate Fokker-Planck PDE in \cite{wang2013fokker} was solved via finite element discretization, and revealed rich stochastic dynamics and nontrivial transient stability aspects even in this simple case. However, it is unreasonable to expect that a finite element discretization, or in fact any spatial discretization scheme to solve (\ref{KineticFPK}) for moderately large $n$ in {\red{minutes}} of computational time, thereby limiting our current ability for realistic power systems simulation with stochastic variability. This calls for fundamentally re-thinking what does it mean to solve the PDE (\ref{KineticFPK}) for dynamics (\ref{ItoSDEvectorlevel}).

@@

\section{Numerical Simulations}\label{sec:NumericalSimulations}
To illustrate the proposed computational framework, we next provide two numerical simulation case studies. In Sec. \ref{subsec:NumSimIEEEBus}, we consider the prediction of stochastic states for the IEEE 14 bus system--{\red{our main objective being to highlight the interpretability and utility of the proposed method in power systems engineering}}. In Sec. \ref{subsec:NumSimSynthetic}, we propagate the joint PDFs over the {\red{100 dimensional state space}} of a synthetic power network with randomly generated parameters--our intent there is to highlight the scalability of the proposed method.

@@

Fig. \ref{fig:CompTimeSynthetic} highlights that for computing high dimensional transient joint state PDFs as in here, the proposed variational framework enjoys remarkably fast computational time. Notice that constructing histograms or other conventional density estimators for the joint state PDF by making a grid over the 40 dimensional state space, is computationally prohibitive.

>>>>

We mention here that (\ref{ItoSDEvectorlevel}) has been used in \cite{ju2018analytical,ju2018stochastic} for uncertainty propagation via stochastic averaging approximation where the univariate energy PDF was proposed as a ``proxy" for the entire joint PDF. Most relevant to our approach in the power systems literature is the work in \cite{wang2013fokker}, which indeed voiced the need for computing the transient joint PDFs but only dealt with the single-machine-infinite-bus case -- simplest ($n=1$) instance of (\ref{ItoSDEvectorlevel}). The resulting bivariate Fokker-Planck PDE in \cite{wang2013fokker} was solved via finite element discretization, and revealed rich stochastic dynamics and nontrivial transient stability aspects even in this simple case. However, it is unreasonable to expect that a finite element discretization, or in fact any spatial discretization scheme to solve (\ref{KineticFPK}) for moderately large $n$ in seconds of computational time, thereby limiting our current ability for realistic power systems simulation with stochastic variability. This calls for fundamentally re-thinking what does it mean to solve the PDE (\ref{KineticFPK}) for dynamics (\ref{ItoSDEvectorlevel}).

@@

\section{Numerical Simulations}\label{sec:NumericalSimulations}
To illustrate the proposed computational framework, we next provide two numerical simulation case studies. In Sec. \ref{subsec:NumSimIEEEBus}, we consider the prediction of stochastic states for the IEEE 14 bus system--{\red{our main objective being to highlight the interpretability and utility of the proposed method in power systems engineering}}. In Sec. \ref{subsec:NumSimSynthetic}, we propagate the joint PDFs over the 100 dimensional state space of a synthetic power network with randomly generated parameters--our intent there is to highlight the scalability of the proposed method.

@@

Fig. \ref{fig:CompTimeSynthetic} highlights that for computing high dimensional transient joint state PDFs as in here, the proposed variational framework enjoys remarkably fast computational time. Notice that constructing histograms or other conventional density estimators for the joint state PDF by making a grid over the 100 dimensional state space, is computationally prohibitive.
